\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-24 paper.tex
Update on Overleaf.

\subsection*{Relation to existing robotic middlewares}

Like traditional robotic middlewares, \uwds offers a form of distributed
computation based on message passing. However, it distinguishes itself from
existing middleware in several significant ways.

First and foremost, \uwds purposefully does not offer any \emph{general}
capability at distributing computation and data flows amongst independent
components: it focuses specifically on distributing environment models, both
spatial (geometric models) and temporal (events and situations).

While using standard middlewares as \emph{underlying transport} for \uwds would be
technically feasible and relatively easy to implement, it does not offer any
clear advantage over lighter and dedicated message passing libraries like ZeroMQ
or gRPC (the later being the one used by \uwds).

@@

i will finish this section later today
...needs for spatial representation

>>>>

\subsection{Relation to existing robotic middlewares}

@@

i will finish it later today
...needs for spatial representation
